---
title: "Assignment 4"
author: "Suyeon Ryu"
date: '2020 11 4'
output: html_document
---
# HPC

## Problem 1: Make sure your code is nice
Rewrite the following R functions to make them faster. It is OK (and recommended) to take a look at Stackoverflow and Google


```{r,include=FALSE}

library(data.table)
library(tidyverse)
library(dplyr)
library(plotly)
library(DT)
library(knitr)


library(microbenchmark)
library(parallel)

```


```{r}


# Total row sums
fun1 <- function(mat){
  n <- nrow(mat)
  ans <- double(n) 
  for (i in 1:n) {
    ans[i] <- sum(mat[i, ])
  }
  ans
}



fun1alt <- function(mat) {
   rowSums(mat)
  }
  
  

# Cumulative sum by row
  
fun2 <- function(mat) {
  n <- nrow(mat)
  k <- ncol(mat)
  ans <- mat
  for (i in 1:n) {
    for (j in 2:k) {
      ans[i,j] <- mat[i, j] + ans[i, j - 1]
    }
  }
  ans
}



fun2alt <- function(mat) {
  asdf <- as.data.table(t(mat))
  asdf <- cumsum(asdf)
  asdf <- t(asdf)
  asdf
}





# Use the data with this code

set.seed(2315)
dat <- matrix(rnorm(200 * 100), nrow = 200)




# Test for the first
microbenchmark::microbenchmark(
  fun1(dat),
  fun1alt(dat), unit = "relative", check = "equivalent"
)

# Test for the second
microbenchmark::microbenchmark(
  fun2(dat),
  fun2alt(dat), unit = "relative", check = "equivalent"
)
```



With new function, it was about 4.8 times faster for the first part. 









## Problem 2: Make things run faster with parallel computing

```{r, include=FALSE}

#The following function allows simulating PI

sim_pi <- function(n = 1000, i = NULL) {
  p <- matrix(runif(n*2), ncol = 2)
  mean(rowSums(p^2) < 1) * 4
}

# Here is an example of the run
##set.seed(156)
##sim_pi(1000) # 3.132

# In order to get accurate estimates, we can run this function multiple times, with the following code:

# This runs the simulation a 4,000 times, each with 10,000 points
set.seed(1231)
system.time({
  ans <- unlist(lapply(1:4000, sim_pi, n = 10000))
  print(mean(ans))
})

# Rewrite the previous code using parLapply() to make it run faster. Make sure you set the seed using clusterSetRNGStream():

## make cluster 

  clust <- makeCluster(4L)
  clusterSetRNGStream(clust, iseed=1231)

  system.time({
  ans2 <- unlist(parLapply(clust, 1:4000, sim_pi, n=10000))
  print(mean(ans2))
  })

  stopCluster(clust)

```

Using parallel computing, the user time was decreased from 3.66 to 0.01, and elapsed time decreased from 3.72 to 1.92.




# SQL
Setup a temporary database by running the following chunk

```{r, include=FALSE}

# install.packages(c("RSQLite", "DBI"))

library(RSQLite)
library(DBI)

# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
film <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film.csv")
film_category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film_category.csv")
category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/category.csv")

# Copy data.frames to database
dbWriteTable(con, "film", film)
dbWriteTable(con, "film_category", film_category)
dbWriteTable(con, "category", category)

#When you write a new chunk, remember to replace the r with sql, connection=con. Some of these questions will reqruire you to use an inner join. Read more about them here https://www.w3schools.com/sql/sql_join_inner.asp

```




## Question 1
How many many movies is there avaliable in each rating catagory.
```{sql, connection = con}

SELECT rating,
 COUNT (film_id) AS Count
FROM film
GROUP BY rating


```



## Question 2
What is the average replacement cost and rental rate for each rating category.
```{sql, connection = con}

SELECT rating,
AVG(replacement_cost) AS avg_replacement_cost,
AVG(rental_rate) AS avg_rental_rate
FROM film
GROUP BY rating

```


## Question 3
Use table film_category together with film to find the how many films there are witth each category ID
```{sql, connection = con}

SELECT film_category.category_id,
  COUNT(*) AS count
FROM film_category JOIN film
GROUP BY category_id
ORDER BY count DESC


```


## Question 4
Incorporate table category into the answer to the previous question to find the name of the most popular category.

```{sql, connection = con}

SELECT film_category.category_id,category.name,
  COUNT(*) AS count
FROM film_category
  INNER JOIN film ON film_category.film_id=film.film_id
  INNER JOIN category ON film_category.category_id=category.category_id
GROUP BY category.category_id
ORDER BY count DESC



```

